Title Goes Here

### 2020-02-25 paper/paper.tex
Improved example

In the example below, \ttt{example} would get transformed into \ttt{example'}:

@@

example :: Int
example =
  case x of
    Left  c -> ord c
    Right i -> i

>>>>

In the example below, the Core plugin transforms \ttt{example} into \ttt{example'}:

@@

example :: Int
example =
  internalize (externalize
    (case x of
      Left  c -> ord c
      Right i -> i))
